### 2020-06-08 chapters/introduction.tex
...

\section{Context} \label{sec:context}
In the past decade, applications have become increasingly data-driven, placing data at the center of application design. Different use cases process data in different ways for different purposes. For instance, e-commerce platforms need to process a large number of transactions, for example, those made daily by all Alibaba's clients, while ensuring that sales run smoothly and that products are delivered to customers' homes. Streaming services, like YouTube and Netflix, try to guarantee that media content reaches up to millions of users simultaneously. Furthermore, this media content may have been previously recorded and stored, or may be generated on the fly. Social networks are also responsible for generating large volumes of data. A social network like Twitter, for example, generates more than 500 million \textit{tweets} (posts in Twitter) per day \cite{twitter-throughput}. \textit{Tweets} may contain text, media content or both. Cybersecurity applications are yet another example of time-sensitive, data-driven applications. These need to monitor user accesses and their actions in the network, where timely detection of intruders is critical to prevent them from tampering with the protected system.

All of these applications generate large volumes of data over time which poses data storage and processing challenges. This data is characterized in terms of its large volume, high velocity and high variety \cite{Mavragani-GoogleTrends-SLR}, creating large scale data management problems. Additionally, the large amounts of information produced by such systems and use-cases lead to the creation of multiple real-time unbounded data sets, also known as data streams. The information that flows through such a stream can be analyzed on-the-fly or stored for later processing. The former case is best known as stream processing, while the latter as batch processing. E-commerce applications have to process endless streams of credit card transactions. Live streaming services need to distribute the media content created by the \textit{streamer} (content creator) and deliver it across multiple users. Social networks process and analyze hundreds of posts per second to find out trending keywords across their network and suggest them to users. Computer network monitor systems want to detect intruders and revoke them system access before they have time to corrupt the system or steal private information. All of the previously given use cases rely on real-time processing of data for near real-time actions. Hence, between batch and stream processing, the latter fits these use cases better.

As mentioned, the processing of data can be divided into two main categories: batch and stream processing. However, due to the increasing volume of data and the need for timely processing to allow companies to react to changing conditions in real-time, stream processing demand is increasing. Data stream processing refers to the handling of huge volumes of high variety of data generated at high-velocity from multiple sources in real-time. Unlike batch processing on static data sets, where assumptions on the underlying data distribution can be made, streaming data is known for being non-stationary \cite{Gama-Knowledge-Discovery}. Furthermore, in the streaming paradigm, the value of the produced information lies in its recency \cite{Kolajo-Big-data-stream-SLR}. \textit{Recency} is measured under different scales for different use cases. For instance, considering the monitoring of geological data to forecast possible natural disasters such as earthquakes versus the monitoring of a computer network for intruder detection. In the former case, after the forecast of a future earthquake, governmental authorities need a couple of days to launch an evacuation plan and keep the population safe. However, in the intruder detection scenario, the decision of removing access to a user must be done as soon as possible, preferably in a few seconds. Hence, while in the first scenario information retrieved within a day would still be recent, in the second scenario, information is considered recent and relevant if delivered within seconds (or even milliseconds).

Both in batch and stream processing, we usually want to apply operations on data, for example, to compute the maximum value, an average or a count of distinct elements. Operations applied to data sets that produce a single result are commonly known as aggregate operations. In stream processing, we apply these aggregations to data streams to obtain valuable information. However, since a data stream is, effectively speaking, an unbounded data set, if our aggregation requires a finite domain, there is the need to apply windowing techniques. A thorough analysis to stream windowing techniques is done in the Background Section of this document but for now it suffices to say that windowing transforms an unbounded data stream into a finite data set by defining a time or tuple-based window size --- \textit{i.e.} events from the last three days or the last million events, respectively.

Consider the case is the detection of credit card fraud on the data stream of all the transactions made on Amazon by every US citizen on a single day. In this case, Amazon's transaction stream will need to be monitored by another system, a fraud detection one. Such a system would have to process all the incoming transactions and decide in a fraction of a second if it is a fraudulent one or not. It is clear that manually monitoring such an intensive, latency-sensitive data stream is hard and error-prone. Thus justifying the need for autonomous real-time data stream monitoring systems.

Many market solutions monitor streams of credit card transactions with the intent of fraud detection. In the context of this Thesis, we will work side by side with Feedzai. Feedzai offers fraud prevention solutions for the previously presented use case of monitoring an infinite stream of credit card transactions and detecting fraud. We will work with them, taking advantage of the multiple real-life data sets they can provide from the financial fraud space.

>>>>

\section{Context} \label{sec:context}
In the past decade, applications have become increasingly data-driven, placing data at the center of application design. Different use cases process data in different ways for different purposes. For instance, e-commerce platforms need to process a large number of transactions, for example, those made daily by all Alibaba's\footnote{https://alibaba.com} clients, while ensuring that sales run smoothly and that products are delivered to customers' homes. Streaming services, like YouTube\footnote{https://youtube.com} and Netflix\footnote{https://netflix.com}, try to guarantee that media content reaches up to millions of users simultaneously. This media content may have been previously recorded and stored, or may be generated on the fly. Social networks are also responsible for generating large volumes of data. A social network like Twitter\footnote{https://twitter.com}, for example, generates more than 500 million \textit{tweets} (posts in Twitter) per day \cite{twitter-throughput}. \textit{Tweets} may contain text, media content or both. Cybersecurity applications are yet another example of time-sensitive, data-driven applications. These need to monitor user accesses and their actions in the network, where timely detection of intruders is critical to prevent them from tampering with the protected system.

All of these applications generate large volumes of data over time which poses data storage and processing challenges. This data is characterized in terms of its large volume, high velocity and high variety \cite{Mavragani-GoogleTrends-SLR}, creating large scale data management problems. Additionally, the large amounts of information produced by such systems and use-cases lead to the creation of multiple real-time unbounded data sets, also known as data streams. The information that flows through such a stream can be analyzed on-the-fly or stored for later processing. The former case is best known as stream processing, while the latter as batch processing.

E-commerce applications have to process endless streams of credit card transactions. Live streaming services need to distribute the media content created by the \textit{streamer} (content creator) and deliver it across multiple users. Social networks process and analyze hundreds of posts per second to find out trending keywords across their network and suggest them to users. Computer network monitor systems want to detect intruders and revoke them system access before they have time to corrupt the system or steal private information. All of the previously given use cases rely on real-time processing of data for near real-time actions. Hence, between batch and stream processing, the latter fits these use cases better.

As mentioned, the processing of data can be divided into two main categories: batch and stream processing. However, due to the increasing volume of data and the need for timely processing to allow companies to react to changing conditions in real-time, the demand for stream processing systems is increasing. Data stream processing refers to the handling of huge volumes of high variety of data generated at high-velocity from multiple sources in real-time. Unlike batch processing on static data sets, where assumptions on the underlying data distributions can be made, streaming data is known for being non-stationary \cite{Gama-Knowledge-Discovery}. Furthermore, in the streaming paradigm, the value of the produced information lies in its recency \cite{Kolajo-Big-data-stream-SLR}. \textit{Recency} is measured under different scales for different use cases. For instance, considering the monitoring of geological data to forecast possible natural disasters such as earthquakes versus the monitoring of a computer network for intruder detection. In the former case, after the forecast of a future earthquake, governmental authorities need a couple of days to launch an evacuation plan and keep the population safe. However, in the intruder detection scenario, the decision of removing access to a user must be done as soon as possible, preferably in a few seconds. Hence, while in the first scenario information retrieved within a day would still be recent, in the second scenario, information is considered recent and relevant if delivered within seconds (or even milliseconds).

Both in batch and stream processing, we usually want to apply operations on data, for example, to compute the maximum value, an average or a count of distinct elements. Operations applied to data sets that produce a single result are commonly known as aggregate operations. In stream processing, we apply these aggregations to data streams to obtain valuable information. However, since a data stream is, effectively speaking, an unbounded data set, if our aggregation requires a finite domain, there is the need to apply windowing techniques. A thorough analysis of stream windowing techniques is done in the Background Section of this document but for now it suffices to say that windowing transforms an unbounded data stream into a finite data set by defining a time or tuple-based window size --- \textit{i.e.} events from the last three days or the last million events, respectively.

Consider the use-case where we want to detect credit card fraud on the data stream of all the transactions made on Amazon\footnote{https://amazon.com} by every US citizen on a single day. In this case, Amazon's transaction stream will need to be monitored by another system, a fraud detection one. Such a system would have to process all the incoming transactions and decide in a fraction of a second if it is a fraudulent one or not. It is clear that manually monitoring such an intensive, latency-sensitive data stream is hard and error-prone, thus justifying the need for autonomous real-time data stream monitoring systems.

Many market solutions monitor streams of credit card transactions with the intent of fraud detection. In the context of this Thesis, we will work side by side with Feedzai\footnote{https://feedzai.com}. Feedzai offers fraud prevention solutions for the previously presented use case of monitoring an infinite stream of credit card transactions and detecting fraud. We will work with them, taking advantage of the multiple real-life data sets they can provide from the financial fraud space.
